Binocular integration of chromatic and luminance signals

### 2024-04-17 manuscript.qmd
Tweaks to example stimuli

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,36))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

@@

t <- seq(0,1,length=9)
lummod <- sin(t*2*pi)
discstim <- array(0,dim=c(length(t),256,256))

@@

par(mar = c(4,1,1,1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))  
axis(1, at=seq(0,4,4/5), tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
mtext(text = seq(0,250,50), side = 1, at=seq(0,4,4/5), line=0)     
title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

>>>>

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-12,36), ylim=c(-12,36))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Pedestal contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="Threshold (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
axis.break(axis=1,breakpos=-9)

@@

# t <- seq(0,1,length=9)
# manually adjust time points for example discs to compensate for monitor gamma
t <- c(0,0.05,0.25,0.45,0.5,0.55,0.75,0.95,1)
lummod <- sin(t*2*pi)
discstim <- array(0,dim=c(length(t),256,256))

@@

par(mar = c(4,1,1,1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,4), ylim=c(0,4))  
axis(1, at=seq(0,4,4/5), tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
mtext(text = seq(0,250,50), side = 1, at=seq(0,4,4/5), line=0.25, cex=1.5)     
title(xlab="Time (ms)", col.lab=rgb(0,0,0), line=1.8, cex.lab=2)
